Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-11-13 prop_letter.tex
comment fixed

\amr{Rewrite next sentence. Thm 4 assumes infinite
  precision. Question: what happens with finite precision
  intervals. Two thoughts: (1) multiple states will match the
  probab. distribution, (2) for small collections of projectors
  different states will agree with observations; if one looks at all
  projectors it may be the case that no state agrees with all.}

\noindent For general QIVPMs mapping to imprecise intervals, we also
want to seek a simple rule to construct them, and to understand which
states are consistent with them. However, if measurement intervals are
too imprecise, the state consistent with the results of measurements
on some projectors might contradict the state induced by some other
projectors. Indeed we can formally prove that, in general, there may
be \emph{no} state consistent with some arbitrary QIVPM.

>>>>

As the intervals in the image of a QIVPM become less and less sharp,
we expect more and more states to be consistent with it. Indeed, in
the limit, the intervals become \imposs, \necess, and \unknown and
every state is consistent with an assignment that states that its
projections are unknown. There is however a subtlety: as shown in the
theorem below, an arbitrary assignment of intervals to projectors
might be globally inconsistent.

% \noindent For general QIVPMs mapping to imprecise intervals, we also
% want to seek a simple rule to construct them, and to understand which
% states are consistent with them. However, if measurement intervals are
% too imprecise, the state consistent with the results of measurements
% on some projectors might contradict the state induced by some other
% projectors. Indeed we can formally prove that, in general, there may
% be \emph{no} state consistent with some arbitrary QIVPM.
